Hardware-Accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-06-24 paper.tex
Replaced performance table with chart

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  The tests were
run on three different machines with a variety of operating systems (Linux, Mac
OS X) and video cards (ATI, NVIDIA).  Table \ref{performance-table} shows the
results.

\begin{table}
  \centering
  \begin{tabular}{ l r r r }
    \toprule
    Approach & Macbook & Desktop & Workstation\\
    \midrule
    Boolean XOR & 12 & 4 & 38 \\
    Depth-Masking & 12 & 4 & 37 \\
    General Slicing & 12 & 3 & 32 \\
    Optimized Slicing & 3 & 3 & 35 \\
    \bottomrule
  \end{tabular}
  \caption{Performance measurements}
  \label{performance-table}
\end{table}

>>>>

The performance of each approach was measured by using a simple frame counter
showing the number of frames rendered in the previous second.  The tests were
run on three different machines with a variety of operating systems (Linux, Mac
OS X) and video cards (ATI, NVIDIA).  Figure 7.3 shows the results with one
hundred samples.

\begin{figure}
\label{overall-performance-chart}
\centering
\begin{tikzpicture}
\begin{axis}[
    xbar,
    xmin=0,
    xlabel=Frames Per Second,
    enlarge y limits=0.2,
    symbolic y coords={Optimized Slicing, General Slicing, Depth-Masking, Boolean XOR},
    ytick=data
]
\addplot coordinates {
    (2,General Slicing)
    (12,Optimized Slicing)
    (12,Depth-Masking)
    (12,Boolean XOR)
};
\addplot coordinates {
    (32,General Slicing)
    (35,Optimized Slicing)
    (37,Depth-Masking)
    (38,Boolean XOR)
};
\addplot coordinates {
    (3,General Slicing)
    (3,Optimized Slicing)
    (4,Depth-Masking)
    (4,Boolean XOR)
};
\end{axis}
\end{tikzpicture}
\caption{Performance of approaches on three different systems with 100 samples.}
\end{figure}
